### 2021-04-19 architecture.tex
Resolve a comment from R1: Symbol costs

The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric property
that is inexpensive to compute,
such as the number of occurrences in the input problem, or the symbol arity.
In our precedence recommender,
we use a \gls{gcn}-based symbol cost model $c$ in place of the simple symbol property,
\todo[author=R1]{What exactly is the GCN-bases symbol cost? Is it the cost calculated by
the model for each symbol, or are different copies of symbols in different occurrences given
different costs?}
and generate a precedence by sorting the symbols by their predicted costs.
An advantage of this scheme is that sorting is a fast operation.

>>>>

The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric property
that is inexpensive to compute,
such as the number of occurrences in the input problem, or the symbol arity.
In our precedence recommender,
we sort the symbols by their costs $c$ produced by the \acrlong{nn} described in \cref{sec:gcn,sec:output}.
An advantage of this scheme is that sorting is a fast operation.
